Sparse Function Space Representation of Neural Networks for Exploration and Retention

### 2023-05-10 paper/main.tex
starting to fill out background

\section{Background} \label{sec:background}

@@

\begin{itemize}
  \item Show prediction performance in classification: UCI classification results, compare to BNN predictive paper
  \item Fast adapatation in model-based RL: results for cartpole
  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
  \item Possible ablations
  \begin{itemize}
    \item How does number of inducing points affect performance?
  \end{itemize}
  \item How good is the assumption that we can linearise BNN to get NTK?
\end{itemize}

Environments
\begin{itemize}
  \item Compare updated posterior with non updated posterior
  \item Need to show update is fast enough for practical use?
  \begin{itemize}
    \item How frequently can we do the posterior update? Every time step or every $K$ steps?
    \item Update depends on number of inducing points?
    \item What experiments can we show for this? Wall clock time vs planning horizon with different numbers of inducing points?
  \end{itemize}
  \item Is linearising NN mean and using fast updates during episode better than keeping non-linearised mean and not updating?
  \item How does number of inducing points affect performance?
  \begin{itemize}
    \item More inducing points means better approximation but larger computational complexity.
  \end{itemize}
  \item How good is the assumption that we can linearise BNN to get NTK?
  \begin{itemize}
    \item Does model's performance get worse during an episode because linearisation becomes more wrong?
    \item SVGP does't have this issue so compare to SVGP in cartpole?
  \end{itemize}
  \item What length planning horizon to use?
  \begin{itemize}
    \item Too small (e.g. $\Horizon=0$) would mean no exploration?
    \item Can $\Horizon$ be too large?
  \end{itemize}
  \begin{itemize}
  \item Compare for different strategies of making decisions under dynamic model's uncertainty:
    \begin{itemize}
      \item \textbf{Greedy exploitation} \(\pi_{\text{greedy}}\)
      \item \textbf{Hallucinated-UCRL} \(\pi_{\text{HUCRL}}\)
      \item \textbf{Thompson sampling} \(\pi_{\text{TS}}\)
    \end{itemize}
  \end{itemize}
  \item Compare impact of stationary vs non-stationary priors
  \begin{itemize}
    \item First do this with GP
    \item Then try to do with Laplace BNN
  \end{itemize}
  \item Compare impact of function vs weight space
\end{itemize}

@@

\begin{ack}
ASK A ABOUT THIS SECTION:
Aidan Scannell is funded by the Finnish Center for Artificial Intelligence.
\end{ack}

>>>>

\section{Methods} \label{sec:methods}

@@

@@
